% Awesome Source CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/darwiin/awesome-neue-latex-cv
%
% Author:
% Christophe Roger
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)

%Section: Work Experience at the top
\sectionTitle{Work Experience - 15 Years}{\faSuitcase}
%\renewcommand{\labelitemi}{$\bullet$}
\begin{experiences}
  \experience
    {Framestore}   			{Software Engineer}
    {Current} 			{Being part of a team specialized in Location Based Virtual Reality working with Unreal Engine 4 using both Blueprint, C++ and C\#.}
	{09/2019}	 	
	{Montreal}			{
						  \begin{itemize}
							\item Developed new features and resolved multiple issues in the Virtual Production pipeline.
							\item Developed different gameplay mechanisms for Location Based VR project.
							\item Profile and Optimized performances using RenderDoc.
						  \end{itemize}
						 }
   \emptySeparator

  \experience
    {CAE}   				{Software Engineer}
    {09/2019} 			{R\&D for the in house C++ OpenGL engine used within the CAE 7000XR flight simulator designed for commercial and military pilot training.}
	{03/2017}	 	
	{Montreal}			{
						  \begin{itemize}
							\item Reducing the latency of in house AR/VR HMD by 16ms using a Timewarp/Reprojection algorithm.
							\item Simulating the dust for desert helicopter training by developing a GPU particle system that is synchronized across up to 20 rendering nodes.
						  \end{itemize}
						 }
   \emptySeparator
   
   \experience
    {Emergent VR} 			{Software Engineer}
    {09/2016} 				{Helped this startup get funded for 2.2 millions and played a major role in the engineering of their Emergent software for the Oculus Gear VR.}
	{09/2015}	 	
	{San Francisco}			{
						  \begin{itemize}
							\item Optimizing the image stabilization pipeline from 1 hour to 2 minutes by moving different computer vision algorithms to the GPU using OpenGL shaders.
							\item Working on in house OpenCV Panorama stitching algorithm.
						  \end{itemize}
						 }
   \emptySeparator
   
   \experience
    {Google} 				{Technical Leader}
	{09/2015} 			{Started a new development team in Buenos Aires. We grew from 3 to 16 people over 1.5 year and took over 7 projects (C++/C\#/Java/Python) that impacted millions of users.}
	{02/2014}	 	
	{Buenos Aires}			{
						  \begin{itemize}
							\item Organizing/Planning the work for the different releases using their internal tracking software.
							\item Reducing the cost of support for the line of products used to synchronize Microsoft Office with Google Apps by fixing several critical issues.
						  \end{itemize}
						 }
   \emptySeparator
   
   \experience
    {Dreamworks} 			{Software Engineer}
    {01/2012} 				{Contributed to Academy Award winning animation software Premo used in the movies: Kung Fu Panda 2, Puss in Boots, Madagascar 3, etc.}
	{01/2011}	 	
	{Los Angeles}			{
						  \begin{itemize}
							\item Architecturing a C++ SDK for in house Rigging Software.
							\item Improving their SCons build system with optimizations on speed by up to 40\% and binary size by 10000\%.
						  \end{itemize}
						 }
   \emptySeparator
   
   \experience
    {Lucasfilm} 			{Software Engineer}
    {05/2010} 				{Core programmer for an engine that powered four Nintendo DS titles. (Star Wars: The Force Unleashed 2, Jedi Alliance and Republic Heroes). I helped with the shipping of The Secret of Monkey Island 1 \& 2: SE.}
	{01/2007}	 	
	{Singapore}			{
						  \begin{itemize}
							\item A Rendering pipeline for Nintendo DS, iPhone and Windows.
							\item A Maya asset pipeline using MEL and C++ SDK.
							\item A silhouette normal mapping algorithm and a water shader for the Xbox 360.
						  \end{itemize}
						 }
  
\end{experiences}
